An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-11 poly-embed-journal/poly-embed-journal.tex
intro comment
meeting notes

\jessiet{Want these as restatables so the numbering is consistent?}
\begin{theorem}\label{thm:embed-poly-informal}
  Every discrete loss $\ell$ is embedded by some polyhedral loss $L$, and every polyhedral loss $L$ embeds some discrete loss $\ell$.
\end{theorem}

@@

Phase 1: construct $\V$. \jessie{In appendix, try to flesh out phase 1.  Follow (and note) textbook(s) where definitions come from}
\begin{itemize}\setlength{\itemsep}{0pt}
\item Write $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ for some finite set $\hat\V \subseteq \reals^\Y_+$ \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar}
\item Extend to $g(x) = \min_{v\in\hat\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = \infty$ otherwise.  Def $g(0) = 0$.
\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ to be the hypograph of $g$.
\item Let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$.
\item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
\item Let $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\hat \V} \cup \H_\Y$.
\item Then $G = \cap \H$.
\item Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite] \jessie{Why is $G$ full-dimensional?}
\item Hence, there is some unique $\H' \subseteq \H$ such that $G = \cap \H'$. \jessie{$\H \subseteq \H$ since $G = \cap \H' = \cap \H$; something about smallest cardinality here?}
\item Argue $\H_\Y \subseteq \H'$.
\item Then $\H' \setminus \H_\Y = \{H_v^+ : v\in\V\} =: \H_\V$ for some $\V \subseteq \hat \V$.
\item That's the $\V$ we are looking for.  (And we've argued that it's uniquely determined by $f$.) \jessie{Why is $\V$ minimum cardinality?}
\item Moreover, $F_v := H_v^+ \cap G$ is a facet of $G$ for each $v\in\V$. \jessie{How do we get from uniquely determined to facet?}
\item Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
\item Show that $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+$. \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
\item Note: $\theta(v) = \pi(F_v) \cap \simplex$.
\end{itemize}

Phase 2: Now given a loss $L:\R\to\reals^\Y_+$ with $\risk L = f$.
\begin{itemize}\setlength{\itemsep}{0pt}
\item Define $\hat\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$.  Unlike above, these could be infinite sets.
\item Let $\H = \H_\Y \cup \H_{\hat \V}$.
\item We once again have $G = \cap\H$ by definition of $\risk{L}$ \raf{prove}
\item Argue that $\H_\V \subseteq \H$, since $\H_\Y \cup \H_\V$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
\item Conclude there is some set $\R^* \subseteq \R$ such that $L(\R^*) = \V$ (without duplicates).
\item Let $r$ be a report, and let $\hat v = L(r)$.
\item As $H_{\hat v}^+ \in \H$, it supports $G$ or it is redundant in $\H$ (or both).
\item If it does support $G$, then $F_{\hat v} = H_{\hat v}^+ \cap G$ is a face of $G$, and thus a subset of a facet.
\item Argue that $F_{\hat v}$ must be a subset of one of the $\V$ facets $F_v$ (as opposed to the vertical ones)
\item Thus, $\pi(F_{\hat v}) \subseteq \pi(F_v)$. \raf{This will show (3) once we translate back}
\item Claim: $\R'$ is a rep set for $L$ if and only if $\V \subseteq L(\R')$.
\item Corollary: $\R^*$ is a min rep set for $L$ if and only if $\V = L(\R^*)$. \raf{(1)}
\item Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
\end{itemize}

@@

>>>>

\jessiet{Want these as restatables so the numbering is consistent?}
\raft{I think good as-is, since in both cases these follow from more specific results}
\begin{theorem}\label{thm:embed-poly-informal}
  Every discrete loss $\ell$ is embedded by some polyhedral loss $L$, and every polyhedral loss $L$ embeds some discrete loss $\ell$.
\end{theorem}

@@

@@

\section{``Book chapter'' approach}

\subsection{Phase 1: construct $\V$}

Set up notation and define $g,G$
\begin{itemize}\setlength{\itemsep}{0pt}
\item Let $f:\simplex\to\reals_+$ be a polyhedral concave function.
\item Claim: we may write $f(p) = \min_{v\in\hat\V} \inprod{p}{v}$ for some finite set $\hat\V \subseteq \reals^\Y_+$ \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
\item Extend to $g(x) = \min_{v\in\hat\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = -\infty$ otherwise.  Def $g(0) = 0$.
\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ to be the hypograph of $g$.
\item For any $v\in\reals^\Y_+$, let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$ and $H_v := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c = 0\}$.
\item Let $H_y^+ := \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
\item Let $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\hat \V} \cup \H_\Y$.
\item Then $G = \cap \H$.
\end{itemize}

Some statements about facets and H-rep
\begin{itemize}
\item Claim: $G$ is $(|\Y|+1)$-dimensional.  \raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
\item \raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite].
  Hence, there is some unique $\H' \subseteq \H$ such that $G = \cap \H'$. \jessie{$\H \subseteq \H$ since $G = \cap \H' = \cap \H$; something about smallest cardinality here?}
  Moreover, each $H\in\H'$ defines a facet \raf{make formal}
\item Claim: $\H_\Y \subseteq \H'$.
\item Then $\H' \setminus \H_\Y = \{H_v^+ : v\in\V\} =: \H_\V$ for some $\V \subseteq \hat \V$; That's the $\V$ we are looking for.  (And we've argued that it's uniquely determined by $f$.) \jessie{Why is $\V$ minimum cardinality?}
\item Define $F_v := H_v \cap G$ for any $v\in\reals^\Y_+$.
\item Claim: $F_v$ is a facet of $G$ for each $v\in\V$.  \raf{Unpacking ``defines a facet''}
\end{itemize}

Projections to the positive orthant
\begin{itemize}
\item Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
\item Claim: For all $x\in\reals^\Y_+$, there exists $v\in\V$ such that $H_v$ supports $G$ at $(x,g(x))$.
\item Corollary: $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+$. \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
\item Note: $\theta(v) = \pi(F_v) \cap \simplex$. \raf{But haven't def $\theta$ yet}
\end{itemize}

\subsection{Phase 2: Now given a minimizable loss $L:\R\to\reals^\Y_+$ with $\risk L = f$.}
\begin{itemize}\setlength{\itemsep}{0pt}
\item Define $\hat\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$.  Unlike above, these could be infinite sets.
\item Let $\H = \H_\Y \cup \H_{\hat \V}$.
\item We once again have $G = \cap\H$ by definition of $\risk{L}$ \raf{prove}
\item Argue that $\H_\V \subseteq \H$, since $\H_\Y \cup \H_\V$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
\item Conclude there is some set $\R^* \subseteq \R$ such that $L(\R^*) = \V$ (without duplicates).
\item Claim: for all $v\in\reals^\Y_+$, if $H_v$ supports $G$,  $\dim(\pi(F_v)) = \dim(F_v)-1$.
\item Let $r$ be a report, and let $\hat v = L(r)$.
\item As $H_{\hat v}^+ \in \H$, it supports $G$ or it is redundant in $\H$ (or both).
\item If it does support $G$, then $F_{\hat v} = H_{\hat v}^+ \cap G$ is a face of $G$, and thus a subset of a facet.
\item Argue that $F_{\hat v}$ must be a subset of one of the $\V$ facets $F_v$ (as opposed to the vertical ones)
\item Thus, $\pi(F_{\hat v}) \subseteq \pi(F_v)$. \raf{This will show (3) once we translate back}
\item Claim: $\R'$ is a rep set for $L$ if and only if $\V \subseteq L(\R')$.
\item Corollary: $\R^*$ is a min rep set for $L$ if and only if $\V = L(\R^*)$. \raf{(1)}
\item Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
\end{itemize}
